\chapter{Introduction}\label{ch:intro}
%these sections are optional, up-to the author
\section{Motivation}
At the moment, a culture of environmental friendliness and re-consumption of things is gradually being formed in Kazakhstan, and second-hand is one of such cultures. Our main motivation is to contribute to this direction and develop people's conscious approach to buying clothes. 
If we rely on global statistics, the fashion industry is one of the industries that pollute the environment and is in second place in terms of consumption after water. Over the past 15 years \cite{stylerbc}, the volume of textile production has doubled. According to Greenpeace, 400,000,000,000 m2 of clothing and accessories are produced annually in the world, of which 60,000,000,000 sq.m is thrown away during the year\cite{greenpeace}. 

Also, modern fashion comes to the fact that people want to wear unique and rare clothes that are difficult to find in the mass market. In an ordinary branded store, all clothes meet the fashion standards of the season. And in the second-hand, it is different and has nothing to do with current trends. This attracts many people, because they experiment and create their own style based on personal preferences. Second-hand makes it possible for people to combine fashion and environmental friendliness.

Now there are more than 150 second-hand shops in Almaty and they have a sufficient number of customers. It is becoming a trend to find and wear unique items at an affordable price in second-hand stores. But this is implemented through direct interaction in the store or through social networks (mainly Instagram), which is not convenient at a time when people are used to making purchases online in a couple of clicks. We want to create a single platform for sellers and buyers to make it easier for everyone to purchase and distribute second-hand clothing.


\section{Aims and Objectives}
Our goal is to centralize second-hand stores. To make life easier for both sellers and buyers. Saving them time and power. Because of that, we decided to make an application to help sellers and customers. So that, it would not only be the target place, it would have a special feature - an auction, so that sellers could make auctions for the items they would consider not usual. And customers would be able to buy the items that they want.

And our objective was to develop a user-friendly web-site with unusual features for our place. We consider to continue to develop this project in the future, so that many other options will be available. We are hoping that our project will be helpful for the people and more convenient for people.

\section{Thesis Outline}
Our thesis contains a total of 5 chapters, where we are explaining every step of our project. The 1st Chapter is Introduction. It says about our motives and goals of our project. The next part is project details. The third part describes project architecture. Chapter 4 is about implementation of the project, what was used, how we used the technologies, etc. Chapter 5 is the conclusion, where summarized all the work that has been done and about future goals of the project. 

